---
title: "Energy Sector of India"
author: 'Rajendra Kujur'
date: "26/06/2022"
output: pdf_document
geometry: left=1cm,right=1cm,top=1.5cm,bottom=1.5cm
---

```{r,echo = FALSE, warning=FALSE,message=FALSE}
library("tidyverse")
library("xlsx")
library("knitr")
library("hrbrthemes")
library("viridis")
library("ggthemes")
library("extrafont")
library("sf")
library("showtext")
library("treemap")
library("RColorBrewer")
library("sunburstR")
library("ggridges")
library("wesanderson")
library("scales")
library("CGPfunctions")
library("plotly")
theme_update(plot.title = element_text(hjust = 0.5))
knitr::opts_chunk$set(warning = FALSE, echo = FALSE,message = FALSE)
knitr::opts_chunk$set(fig.width=10, fig.height=8)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

# ENERGY DISTRIBUTION IN INDIA ON THE BASIS OF ELECTRICITY GENERATION

```{r}
dataEnergyBySource<-read.csv(file = "./Data/Electricity Generation by Source_D_2.csv", header = T)

dataEnergyBySource<-dataEnergyBySource[-c(5,10),]

dataEnergyBySource$EnergySource[6] = "BIOMASS"

treemap(dataEnergyBySource, index=c("EnergySource"), vSize="Generation_GWh", vColor= "EnergySource", type="index", palette =  "RdYlGn", fontsize.labels = c(10,10), title = "Energy distribution in Inda")

```


# PIE CHART

```{r}
dataEnergyBySource$DiscreteCapacity<-round(dataEnergyBySource$Generation_GWh)

dataEnergyBySource$DiscreteCapacitypercent<-dataEnergyBySource$DiscreteCapacity/sum(dataEnergyBySource$DiscreteCapacity)

fig <- plot_ly(dataEnergyBySource, labels = ~EnergySource, values = ~DiscreteCapacitypercent, type = 'pie')

fig <- fig %>% layout(title = "Energy Distribution in India",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


is_pdf <- try (("pdf_document" %in% rmarkdown::all_output_formats(knitr::current_input())), silent=TRUE)
is_pdf <- (is_pdf == TRUE)

if (is_pdf) { export(fig) } else {fig}

```


# ALL INDIA SECTOR WISE

```{r}

dataAllIndiaSector<-read.xlsx(file = "./Data/All India Sectorwise Installed Capacity Installed Generation Capacity.xlsx", sheetIndex = 1, startRow = 1)

regionNames<-c("Sector", "Northeren Region", "Westeren Region", "Southeren Region", "Easteren Region", "North Easteren Region", "All India")

colnames(dataAllIndiaSector)<-regionNames

dataAllIndiaSectorLongFormat<-dataAllIndiaSector%>%gather(REGIONS, CapacityinMW, -c(Sector))

dataAllIndiaSectorLongFormatWOallIndia<-dataAllIndiaSectorLongFormat[dataAllIndiaSectorLongFormat$REGIONS != "All India",]

dataAllIndiaSectorLongFormatWOtotal<-dataAllIndiaSectorLongFormatWOallIndia[dataAllIndiaSectorLongFormatWOallIndia$Sector != "Total",]

ggplot(dataAllIndiaSectorLongFormatWOtotal, mapping = aes(x = REGIONS, y = CapacityinMW)) + geom_bar(mapping = aes(color = Sector, fill = Sector),position = "dodge",stat = "identity", width = 0.5)+scale_color_brewer(palette = "Accent") + scale_fill_brewer(palette = "Accent") + theme_clean() + theme(axis.text.x = element_text(angle=0, vjust=0.6)) + labs(title ="All India electriciy distribution region wise" ,x = "Regions of India", y = "Electrical Capacity in MW")+
  theme(plot.title = element_text(hjust = 0.5))
```



# MODE WISE DATA


```{r}
dataModeWise<-read.xlsx(file = "./Data/Daily data on sector wise and Mode wise Installed Capacity.xlsx", sheetIndex = 1, startRow = 1)

ggplot(data = dataModeWise, mapping = aes(x = reorder(State, -Installed.Capacity),y = Installed.Capacity)) + geom_bar(mapping = aes(color = Mode, fill = Mode), stat = "identity", width = 0.5) +scale_color_brewer(palette = "Accent",direction = -1, name = "Mode", labels = c("HYDRO", "NUCLEAR", "RENEWABLE ENERGY SOURCE", "THERMAL"))+scale_fill_brewer(palette = "Accent",direction = -1, name = "Mode", labels = c("HYDRO", "NUCLEAR", "RENEWABLE ENERGY SOURCE", "THERMAL")) + theme_clean() + theme(axis.text.x = element_text(angle = 90)) + labs(title ="Distribution of electricity in all states mode wise" ,x = "States of India", y = "Electrical Capacity in MW")+
  theme(plot.title = element_text(hjust = 0.5))
```


# SOURCE WISE DATA


```{r}
dataSourceWise<-read.xlsx(file = "./Data/Source-wise Installed Generation Capacity.xlsx", sheetIndex = 1, startRow = 1)

dataSourceWise$Generation.Capacity..MW.<-as.numeric(dataSourceWise$Generation.Capacity..MW.)

dataSourceWise<-na.omit(dataSourceWise)

dataSourceWiseWOtotal<-dataSourceWise[-c(5,13,14), ]

dataSourceWiseWOtotal$Id<-c(seq(1,11,1))

rownames(dataSourceWiseWOtotal)<-dataSourceWiseWOtotal$Id
dataSourceWiseWOtotal[9,"Source.Fuel"]<-"Biomass"
dataSourceWiseWOtotal[10,"Source.Fuel"]<-"Waste to Energy"
dataSourceWiseWOtotal[11,"Source.Fuel"]<-"Waste to Energy"

dataSourceWiseWOtotal[11,3]<-dataSourceWiseWOtotal[10,3] + dataSourceWiseWOtotal[11,3]

dataSourceWiseWOtotal<-dataSourceWiseWOtotal[-10,]

dataSourceWiseWOtotal$percentageCategory<-dataSourceWiseWOtotal$Generation.Capacity..MW./sum(dataSourceWiseWOtotal$Generation.Capacity..MW.)


mycolors <- c(brewer.pal(name="Accent", n = 8), brewer.pal(name="Spectral", n = 6))

ggplot(dataSourceWiseWOtotal, mapping = aes(x = Category, y = percentageCategory)) + geom_bar(mapping = aes(color =  Source.Fuel, fill = Source.Fuel),stat = "identity", width = 0.5)+scale_color_manual(values = mycolors, name = "SOURCES OF FUEL", labels = c("BIOMASS", "COAL", "DIESEL", "NATURAL GAS", "HYDRO", "LIGNITE", "NUCLEAR", "SMALL HYDRO POWER", "WASTE TO ENERGY", "WIND"))+scale_fill_manual(values = mycolors,name = "SOURCES OF FUEL", labels = c("BIOMASS", "COAL", "DIESEL", "NATURAL GAS", "HYDRO", "LIGNITE", "NUCLEAR", "SMALL HYDRO POWER", "WASTE TO ENERGY", "WIND")) + labs(title ="Distribution of electricity in India by sources" ,x = "Sources of Electricity", y = "Electrical Capacity in percentage",color = "Sources of Fuel", fill = "Sources of Fuel")+
  theme(plot.title = element_text(hjust = 0.5)) + scale_y_percent()
```

# COMPARISON BETWEEN DIFFERENT TYPES OF FUEL SOURCE USED

```{r,warning=FALSE,message=FALSE}
dataGenerationBySource<-read.csv(file = "./Data/Electricity Generation by Source_D_20210409_233241.CSV", header = T)

mycolors <- c(brewer.pal(name="Accent", n = 8), brewer.pal(name="Dark2", n = 6))

ggplot(dataGenerationBySource, aes(x = YearValue, y = Generation_GWh, fill = EnergySource)) + geom_area(alpha=0.6 , size=.5, colour="white")+ scale_x_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2))) + scale_fill_manual(values = mycolors, name = "Energy Source") + labs(title = "Comparison between different source of fuels", x = "Year", y = "Generation in GWh") + theme_clean()+ theme(legend.position = "bottom",plot.title = element_text(hjust = 0.5))
```

# COAL RESERVES IN INDIA

```{r}
states_shape<-rgdal::readOGR("./Data/IND_adm1.shp")

dataCoalReserve2019<-read.csv(file = "./Data/Coal Reserves by State_D_1_NAMECHANGED.csv",header =T)

State_data = data.frame(id=states_shape$ID_1, NAME_1=states_shape$NAME_1, dataCoalReserve2019)

fortify_shape = fortify(states_shape, region = "ID_1")

Merged_data <- merge(fortify_shape, State_data, by="id", all.x=TRUE)
Map_plot1 = Merged_data[order(Merged_data$order), ]


ggplot() +
  geom_polygon(data = Map_plot1,
               aes(x = long, y = lat, group = group, fill = QtyInMillionTonnes),color = "black", size = 0.3) + coord_map() + scale_fill_gradient(low="white", high="brown") + theme_void()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title = "Coal reserves in India", color = "Quantity in Million tonnes", fill = "Quantity in Million tonnes")

```


# COAL CONSUMPTION BY EACH STATE

```{r}
dataCoalConusmp2019<-read.csv(file = "./Data/Coal Consumption - Domestic by State_D_1.csv")

dataCoalConusmp2019[,3]<-round(dataCoalConusmp2019[,3],0)

dataCoalConusmp2019<-dataCoalConusmp2019[-24,]

dataCoalConusmp2019<-dataCoalConusmp2019[,-c(1)]

dataCoalConusmp2019 %>%
  arrange(dataCoalConusmp2019$QtyInMillionTonnes)%>% mutate(name=factor(State, levels=State))%>% ggplot( aes(x=name, y=QtyInMillionTonnes)) +
  geom_segment( aes(xend=name, yend=0)) +
  geom_point( size=4, color="darkgreen") +
  coord_flip() +
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title ="Coal consumption by different states" ,x = "States of India", y = "Quantity in Million Tonnes")
```

# SLOPE GRAPH

```{r}
databySource2009<-read.csv(file = "./Data/Electricity Generation by State_D_2009.csv", header = T)

databySource2009<-databySource2009[databySource2009$UtilityCaptive == "UTILITY",]

b<-c("UTTAR PRADESH","MADHYA PRADESH", "MAHARASHTRA", "CHHATTISGARH" )

a<-databySource2009[databySource2009$State %in% b,]
ca<-a[,-c(1,3,5,6,8)]


da <-ca%>%group_by(State,EnergySource) %>% summarize(Generation_GWh = sum(Generation_GWh))

dawide<-spread(da,EnergySource,Generation_GWh)

dawide[is.na(dawide)]<-0

dawide$Year<-rep(2009,4)


databySource2019<-read.csv(file = "./Data/Electricity Generation by State_D_2019.csv", header = T)

databySource2019<-databySource2019[databySource2019$UtilityCaptive == "UTILITY",]

b<-c("UTTAR PRADESH","MADHYA PRADESH", "MAHARASHTRA", "CHHATTISGARH" )

a1<-databySource2019[databySource2019$State %in% b,]

ca1<-a1[,-c(1,3,5,6,8)]



da1 <-ca1%>%group_by(State,EnergySource) %>% summarize(Generation_GWh = sum(Generation_GWh))

dawide1<-spread(da1,EnergySource,Generation_GWh)

dawide1[is.na(dawide1)]<-0

dawide1$Year<-rep(2019,4)

combinedSlopeData<-rbind(dawide, dawide1)
combinedSlopeData$Year<-as.character(combinedSlopeData$Year)

newggslopegraph(combinedSlopeData, Year, COAL, State, Title = "Electricity from coal", SubTitle = NULL, Caption = NULL,LineThickness = 1,YTextSize = 3,LineColor = c("UTTAR PRADESH" = "darkgreen","MADHYA PRADESH" = "red", "MAHARASHTRA" = "darkblue", "CHHATTISGARH" = "orange")) 
```

# RENEWABLE COMPARISON CAPACITY WISE


```{r}
dataCapacityrenew2019<-read.csv(file = "./Data/Renewable Electricity Capacity by State_D_1 (2).csv", header = T)

dataCapacityrenew2019Total<-dataCapacityrenew2019%>%group_by(State)%>%summarize(Capacity_MW = sum(Capacity_MW))

ggplot(dataCapacityrenew2019Total, mapping = aes(x = reorder(State, -Capacity_MW), y = Capacity_MW)) + geom_bar(fill="darkgreen",stat = "identity", width = 0.5) + theme(axis.text.x = element_text(angle = 90))+ scale_y_continuous(breaks = c(seq(from = 2000, to = 14000, by = 2000)),labels = c(seq(from = 2000, to = 14000, by = 2000))) + labs(title = " Renewable energy among states capacity wise", x = " States of India", y = "Capacity in MW") +
  theme(plot.title = element_text(hjust = 0.5))

```

So now we know Karnataka has the highest renewable energy capacity.\



# RENEWABLE BY SOURCE

```{r}
dataCapacityrenew2019<-read.csv(file = "./Data/Renewable Electricity Capacity by State_D_1 (2).csv", header = T)

dataCapacityrenew2019Source<-dataCapacityrenew2019%>%group_by(EnergySource)%>%summarize(Capacity_MW = sum(Capacity_MW))

dataCapacityrenew2019Source %>%
  arrange(dataCapacityrenew2019Source$Capacity_MW)%>% mutate(name=factor(EnergySource, levels=EnergySource))%>%ggplot(aes(x=EnergySource, y=Capacity_MW)) +
  geom_segment(aes(x=name,xend=name,yend=0)) +
  geom_point( size=4, color="darkorange") +
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title ="Comaparison between different renewable energy sources in India capacity wise" ,x = "Different Renewable Energy types", y = "Capacity in MW")
```

As we get to know the top 2 capacity wise sources in renewable energy are Solar and Wind.\



# WIND ENERGY DISTRUBUTION ON MAP

```{r}
states_shape<-rgdal::readOGR("./Data/IND_adm1.shp")


dataCapacityWind2019Source<-read.csv(file = "./Data/Renewable Electricity Capacity by State_D_1 WIND.csv",header =T)

State_data = data.frame(id=states_shape$ID_1, NAME_1=states_shape$NAME_1, dataCapacityWind2019Source)

fortify_shape = fortify(states_shape, region = "ID_1")

Merged_data <- merge(fortify_shape, State_data, by="id", all.x=TRUE)
Map_plot1 = Merged_data[order(Merged_data$order), ]


ggplot() +
  geom_polygon(data = Map_plot1,
               aes(x = long, y = lat, group = group, fill = Capacity_MW),color = "black", size = 0.3) + coord_map() + scale_fill_gradient(low="white", high="darkblue") + theme_void()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title = "Wind energy capacity in India", color = "Capacity in MW", fill = "Capacity in MW")

```

# SOLAR ENERGY DISTRUBUTION ON MAP


```{r}
states_shape<-rgdal::readOGR("./Data/IND_adm1.shp")


dataCapacitySolar2019Source<-read.csv(file = "./Data/Renewable Electricity Capacity by State_D_1 SOLAR.csv",header =T)

State_data = data.frame(id=states_shape$ID_1, NAME_1=states_shape$NAME_1, dataCapacitySolar2019Source)

fortify_shape = fortify(states_shape, region = "ID_1")

Merged_data <- merge(fortify_shape, State_data, by="id", all.x=TRUE)
Map_plot1 = Merged_data[order(Merged_data$order), ]


ggplot() +
  geom_polygon(data = Map_plot1,
               aes(x = long, y = lat, group = group, fill = Capacity_MW),color = "black", size = 0.3) + coord_map() + scale_fill_gradient(low="white", high="darkorange") + theme_void()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title = "Solar energy capacity in India", color = "Capacity in MW", fill = "Capacity in MW")

```

# GENERATION TREND BY RENEWABLE SOURCE

```{r,warning=FALSE,message=FALSE}
dataGenerationByRenewSource<-read.csv(file = "./Data/Electricity Generation by Source_D_1 (2).CSV", header = T)

options(scipen=150000)
ggplot(dataGenerationByRenewSource, aes(x = YearValue, y = Generation_GWh, fill = EnergySource)) + geom_area(alpha=0.6 , size=.5, colour="white") + scale_x_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2)))+ scale_y_continuous(breaks = c(seq(from = 25000, to = 150000, by = 25000)),labels = c(seq(from = 25000, to = 150000, by = 25000)))+ scale_fill_viridis(discrete = T, name = "Energy Source")+ labs(title = "Comparison between different renewable energy sources", x = "Year", y = "Generation in GWh") + theme_clean()+ theme(legend.position = "bottom",plot.title = element_text(hjust = 0.5))
```


# GENERATION OF RENEWABLE SHOWN ON MAP

And again for the Whole renewable energy, which comprises of all types, we plot it on the Map of India, to see which states dominate in Renewable energy.

```{r}
states_shape<-rgdal::readOGR("./Data/IND_adm1.shp")

dataRenewGeneration2019<-read.csv(file = "./Data/Electricity Generation by State_D_Renew1.csv",header =T)

dataRenewGeneration2019<-dataRenewGeneration2019[-25,]

State_data = data.frame(id=states_shape$ID_1, NAME_1=states_shape$NAME_1, dataRenewGeneration2019)

fortify_shape = fortify(states_shape, region = "ID_1")

Merged_data <- merge(fortify_shape, State_data, by="id", all.x=TRUE)
Map_plot1 = Merged_data[order(Merged_data$order), ]


ggplot() +
  geom_polygon(data = Map_plot1,
               aes(x = long, y = lat, group = group, fill = Generation_GWh),color = "black", size = 0.3) + coord_map() + scale_fill_gradient(low="white", high="darkgreen") + theme_void()+
  theme(plot.title = element_text(hjust = 0.5)) + labs(title = "Renewable electricity overall in India by generation", color = "Generation in GWh", fill = "Generation in GWh")

```


# RENEWABLE COMPARSION GENERATION AND CAPACITY

```{r}
compareData<-read.csv(file = "./Data/COMPARISONRENEWGENCONSUMP - Copy.csv")


thecolors<-c("COLOR1" = "orange", "COLOR2" =  "darkgreen")

ggplot(compareData) +
  geom_segment(aes(x=State, xend=State, y=GENERATION, yend=CAPACITY), color="grey") +
  geom_point(aes(x=State, y=GENERATION),color = "orange", size=2 ) +
  geom_point(aes(x=State, y=CAPACITY),color = "darkgreen", size=2 )+scale_fill_manual(values=thecolors) +
  coord_flip() + theme(plot.title = element_text(hjust = 0.5)) + labs(title = "The Gap among generation and capacity among the states in Renewable energy",y = "Percentage", x ="States of India" ,color = "Generation in GWh", fill = "Generation in GWh")

```


# PER CAPITA STATE WISE

```{r,eval=FALSE}
dataPerCapitaState<-read.csv(file = "./Data/Electricity Consumption per Capita by State_D_CORRECT.csv", header = T)

dataPerCapitaState %>%
  arrange(Consumption_KWh_PerCapita) %>%
  mutate(State = factor(State, State)) %>%
  ggplot(aes(x=State, y=Consumption_KWh_PerCapita , size = Population_Millions)) +
    geom_point(alpha=0.5, color="darkblue") +
    scale_size(range = c(.1, 10), name="Population in Millions")+ theme(axis.text.x = element_text(angle = 90)) + scale_y_log10() +
    scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A") + labs(title = "Per capita consumption for the year 2019", x = "States", y = "Consumption per capita in KWh") + theme(plot.title = element_text(hjust = 0.5))
```

# TOTAL CONSUMPTION STATE WISE IN 2019  

```{r}
wer<-read.csv(file = "./Data/Electricity Consumption by Region_D1_ITEMIZED.csv", header = T)

wer1<-wer%>%group_by(State)%>%summarize(totalConsump = sum(Consumption_GWh))
wer1<-wer1[-19,]

abc1<-read.csv(file = "./Data/abc.csv", header = T)

options(scipen=150000)
abc1 %>%
  arrange(totalConsump) %>%
  mutate(State = factor(State, State)) %>%
  ggplot(aes(x=State, y=totalConsump , size = Population_Millions)) +
  geom_point(alpha=0.5, color="darkblue") +
  scale_size(range = c(.1, 12), name="Population in Millions")+ theme(axis.text.x = element_text(angle = 90)) + scale_y_log10() +
  scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A") + labs(title = "Comparsion with respect to consumption of states for the year 2019", x = "States", y = "Consumption in GWh")+ theme(legend.position = "bottom",axis.text.x = element_text(angle=90, vjust=0.6),plot.title = element_text(hjust = 0.5))


```


# PER CAPITA SHOWN ON THE MAP


```{r}
states_shape<-rgdal::readOGR("./Data/IND_adm1.shp")

perCapita2019<-read.csv(file = "./Data/Electricity Consumption per Capita by State_D_CORRECT.csv",header =T)

perCapita2019$consumptionLogScale<-log10(perCapita2019$Consumption_KWh_PerCapita)

perCapita2019$consumptionNaturalLogScale<-log(perCapita2019$Consumption_KWh_PerCapita)

State_data = data.frame(id=states_shape$ID_1, NAME_1=states_shape$NAME_1, perCapita2019)

fortify_shape = fortify(states_shape, region = "ID_1")

Merged_data <- merge(fortify_shape, State_data, by="id", all.x=TRUE)
Map_plot1 = Merged_data[order(Merged_data$order), ]


ggplot() + geom_polygon(data = Map_plot1,aes(x = long, y = lat, group = group, fill = consumptionNaturalLogScale), size = 0.3) + coord_map() + theme_void() + scale_fill_gradient(low="white", high="darkred")  + labs(title = "Per capita energy consumption in India", color = "Per capita consumption in Kwh converted to log scale", fill = "Per capita consumption in Kwh converted to log scale")+ theme(plot.title = element_text(hjust = 0.5))

```



# CONSUMPTION IN 2019

```{r}
data2019power<-read.csv(file = "./Data/power consumption 2019 state wise.csv")

statestoRemain<-c('Punjab', 'Haryana', 'Rajasthan', 'Delhi', 'UP','Uttarakhand', 'Gujarat','MP', 'Maharashtra','Andhra Pradesh', 'Telangana', 'Karnataka', 'Kerala', 'Tamil Nadu')

data2019powerSomeStates<-data2019power[(data2019power$States%in%statestoRemain), ]

ggplot(data2019powerSomeStates, mapping = aes(x = Usage , y = States, fill = stat(x))) + geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) + scale_fill_viridis_c(name = "Usage", option = "C") + labs(title = "Consumption of various states over the year 2019")+ theme(plot.title = element_text(hjust = 0.5))
```


# PER CAPITA INCREASE FOR THE TOP 4 HIGHEST CONSUMING STATES


```{r}
dataPerCapitaGrowth<-read.csv(file = "./Data/Electricity Consumption per Capita by State_D_GROWTH.csv", header = T)

ggplot(dataPerCapitaGrowth, mapping = aes(x = YearValue, y = Consumption_KWh_PerCapita)) + geom_line(mapping = aes(color = State), alpha = 0.9, size = 1.5, linetype = 1) + geom_point(shape=21, color="black", fill="#69b3a2", size=2) + theme_wsj()+ scale_colour_wsj("colors6") + scale_x_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2))) + scale_y_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2))) + scale_y_continuous()

```

# GROWTH IN ELECTRICTY GENERATION BY STATES OVER THE YEARS

```{r}
dataGenerationByStates<-read.csv(file = "./Data/Electricity Generation by State_D_20.csv", header = T)

ggplot(dataGenerationByStates, mapping = aes(x = YearValue, y = Generation_GWh)) + geom_line(mapping = aes(color = State), alpha = 0.9, size = 1.5, linetype = 1) + geom_point(shape=21, color="black", fill="#69b3a2", size=2) + theme_wsj()+ scale_colour_wsj("colors6") + scale_x_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2))) + scale_y_continuous(breaks = c(seq(from = 2006, to = 2020, by = 2)),labels = c(seq(from = 2006, to = 2020, by = 2))) + scale_y_continuous()
```

# CONSUMPTION BY CONSUMING SECTOR


```{r}
databySector2019<-read.csv(file = "./Data/Electricity Consumption by Consuming Sector_D_NOT ITEMIZED.csv",header = T)

databySector2019$percent<-databySector2019$Consumption_GWh/sum(databySector2019$Consumption_GWh)
  
ggplot(data = databySector2019, mapping = aes(x = ConsumingSector,y = percent))+geom_bar(aes(color = ConsumingSector, fill = ConsumingSector),stat = "identity")+ theme_few() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + labs(title ="Distribution of electricity in india consuming sector  wise" ,x = "Consumers of electricity", y = "Electrical Capacity consumed in percentage") + scale_y_continuous(labels = scales::percent)

```


# STATES COMPARISON OVER INDUSTRIAL AND RESIDENTIAL LOAD

```{r}
dataConsumerSector2019<-read.csv(file = "./Data/Electricity Consumption by Consuming Sector_D_1.csv", header = T)

broadCategory<-c("RESIDENTIAL", "INDUSTRIAL")

dataConsumerSector2019a<-dataConsumerSector2019[dataConsumerSector2019$BroadCategory %in% broadCategory,]

def<-dataConsumerSector2019a %>% group_by(State,BroadCategory)%>%summarize(Consumption_GWh = sum(Consumption_GWh))

def1<-def %>% group_by(State)%>%mutate(percentage = Consumption_GWh/sum(Consumption_GWh))%>%arrange(percentage)

def1<-na.omit(def1)

def1<-def1%>%group_by(State)

ggplot(def1, aes(y = Consumption_GWh,x = State, fill = BroadCategory)) + geom_bar(position = "fill", stat = "identity") + scale_y_continuous(labels = scales::percent) +labs(title = "Comparison between Industrial and Residential load among the states", x = "States of India", y = "Percentage Consumption",fill = "CATEGORY") + coord_flip()

```



# CO2 EMISSIONS PER CAPITA

```{r}
dataCO2emissionpercapita<-read.csv(file = "./Data/co-emissions-per-capita.CSV", header = T)

dataCO2emissionpercapita<-dataCO2emissionpercapita[dataCO2emissionpercapita$Code == "IND",]

ggplot(dataCO2emissionpercapita, mapping = aes(x = Year, y = Per.capita.CO2.emissions)) + geom_line() + labs(title = "CO2 emissons per capita increase over the years of India", x = "Year", y = "Per capita emission in tonnes") + theme_clean()+ theme(plot.title = element_text(hjust = 0.5))
```


# CO2 EMISSION SECTOR WISE


```{r,warning=FALSE,message=FALSE}

dataCO2emissionbyFuelLine<-read.csv(file = "./Data/co2-emissions-by-fuel-line.CSV", header = T)

dataCO2emissionbyFuelLine<-dataCO2emissionbyFuelLine[dataCO2emissionbyFuelLine$Code == "IND",]

dataCO2emissionbyFuelLine<-subset(dataCO2emissionbyFuelLine, select = -c(Entity,Code))

colnames(dataCO2emissionbyFuelLine)<-c("Year","CO2 Emissions from Oil" ,"CO2 Emissions from Flaring","CO2 Emissions from Cement","CO2 Emissions from Coal","CO2 Emissions from Gas","CO2 Emissions from Other Industry")

dataCO2emissionbyFuelLine<-filter(dataCO2emissionbyFuelLine, Year>= 1900 & Year<= 2018)

dataCO2emissionbyFuelLineinLongFormat<-dataCO2emissionbyFuelLine%>%gather(EmissionType, EmissionValue, -c(Year))


dataCO2emissionbyFuelLineinLongFormat$EmissionValue[is.na(dataCO2emissionbyFuelLineinLongFormat$EmissionValue)]<-0

dataCO2emissionbyFuelLineinLongFormat<-na.omit(dataCO2emissionbyFuelLineinLongFormat)

dataCO2emissionbyFuelLineinLongFormat$EmissionType <- factor(dataCO2emissionbyFuelLineinLongFormat$EmissionType , levels=c("CO2 Emissions from Coal", "CO2 Emissions from Oil", "CO2 Emissions from Gas", "CO2 Emissions from Cement", "CO2 Emissions from Other Industry"))

ggplot(dataCO2emissionbyFuelLineinLongFormat, aes(x = Year, y = EmissionValue/10^6, fill = EmissionType)) + geom_area(alpha=0.6 , size=.5, colour="white") + scale_fill_viridis(discrete = T, name = "Emission from source")+ scale_x_continuous(breaks = c(seq(from = 1900, to = 2019, by = 50)),labels = c(seq(from = 1900, to = 2019, by = 50)))+ scale_y_continuous(breaks = c(seq(from = 200, to = 2600, by = 200)),labels = c(seq(from = 200, to = 2600, by = 200))) + labs(title = "Comparision between fuel type based on CO2 emission", x = "Years", y = "Emission in Million Tonnes")+ theme_clean() + theme(plot.title = element_text(hjust = 0.5))
```


# GHG EMISSIONS SECTOR WISE


```{r}
dataGHGemission<-read.csv(file = "./Data/ghg-emissions-by-sector.csv", header = T)

dataGHGemission<-dataGHGemission[dataGHGemission$Code == "IND",]

ghgcompare<-c("Year","Agriculture..GHG.Emissions..CAIT.","Industry..GHG.Emissions..CAIT.","Manufacturing.Construction.energy..GHG.Emissions..CAIT.","Transport..GHG.Emissions..CAIT.","Electricity...Heat..GHG.Emissions..CAIT.")

ghgIndia<-dataGHGemission[,ghgcompare]

ggplot(ghgIndia, aes(x=Year)) + 
  geom_line(aes(y=Agriculture..GHG.Emissions..CAIT./10^9, col="Agriculture")) + 
  geom_line(aes(y=Industry..GHG.Emissions..CAIT./10^9, col="Industry")) +
  geom_line(aes(y=Manufacturing.Construction.energy..GHG.Emissions..CAIT./10^9, col="Construction")) + 
  geom_line(aes(y=Transport..GHG.Emissions..CAIT./10^9, col="Transport")) +
  geom_line(aes(y=Electricity...Heat..GHG.Emissions..CAIT./10^9, col="Electricity")) + scale_color_manual(name="", values = c("Agriculture"="#00ba38", "Industry"="#f8766d","Construction" = "blue", "Transport"="orange","Electricity" ="darkred")) + 
  labs(title="Green house gases emissions by various sectors", x = "Years", y="GHG Emission value in billon tonnes") + scale_y_continuous(breaks = c(seq(from = 0.1, to = 1.8, by = 0.2)),labels = c(seq(from = 0.1, to = 1.8, by = 0.2))) + scale_x_continuous(breaks = c(seq(from = 1990, to = 2016, by = 4)),labels = c(seq(from = 1990, to = 2016, by = 4)))+ theme_clean()

```
