\bigskip  \bigskip \bigskip \bigskip \bigskip \bigskip
\hfill  \hfill \hfill
\Large
\begin{center}
\textbf{ACKNOWLEDGEMENTS}
\end{center}
\bigskip  
\small
This thesis would not have been possible without the help and cooperation of many. I would like to thank the following people who have helped me directly or indirectly to complete my research work and make this thesis. \par \noindent
First and foremost, I would like to thank my project guide \textbf {Dr. P. Venkata Subba Reddy}, Assistant Prof., Dept. of CSE, NIT Warangal, for constantly guiding and encouraging me throughout the entire duration of my project work. He has not only helped me with his technical knowledge but also with his moral values. He has inspired me with his work ethic and his passion for research work. I could not have completed this work without him.   
\par \noindent
I thank the Ministry of Human Resource Development (MHRD), New Delhi, India, for their financial support during my B. Tech. program. I must also thank all the faculty members in the Dept. of CSE, NIT Warangal for their cooperation during my M. Tech. program.
\par \noindent
I am grateful to the following authors and researchers \textbf{J. Cyman, M. Lemanska, J. Raczek} for introducing the concept of doubly connected domination in graphs \cite{dcds} and \textbf{B. H. Arriola, S. R. Canoy} for introducing the concept of secure doubly connected domination in graphs in \cite{sdcds} and also \textbf{S. V. D. Rashmi, S. Arumugam} for introducing the concept of perfect secure domination in graphs in \cite{pscd}.
\par \noindent
Finally I would like to thank my mother \textbf{Laxmidevi} and my father \textbf{Vijay Narayan Gupta}, for believing in me. This project work would not have been possible without their constant support, love and affection.
\vspace{0.25in}
\begin{flushright}
\textbf{(Deepakkumar Vijay Gupta)}
\end{flushright}
\newpage 